EvoSwarm: An Event-based Architecture for Multi-population Optimization Algorithms

### 2020-05-14 draft.tex
Commenty aboout colors in legend
Addressing comment about BBOB experiment

The results obtained by the experiments show (see Figure \ref{fig:bbob}) how
the runtime scales with dimension to reach certain target values $\Delta f$;
The color of the lines indicates the average runtime, for each target reached
at least once. A red circle without a number on top indicates the algorithm
has reached the $10^{-8}$ target on all instances for that dimension. If there
is that number, it indicates how many times the algorithm has reached
the target. Fixed values of targets $\Delta f = 10^{k}$ with $k$ colors are
given in the legend of $f_1$, $k$ values are $[-8,-5,-3,-2,-1,0,1]$. Results
from each configuration are presented in each column, GA, PSO, and GA\&PSO
populations. % clarify which colors for every level - JJ

@@

Finally, the proposed PSO\&GA mixed algorithm has reached the $10^{-8}$ target
value on all functions ($f_1-f_5$) and scales well to higher dimensions, even on
$f_3$ and $f_4$ (charts on the lower rows), which are usually considered
difficult functions. This experiment also exemplifies the type of analyses that
we can perform with the results of the EvoSwarm application by reusing the COCO framework. % If this is what you want to prove, it's not a very strong point. Maybe it would be stronger if you proved that these mixed algorithms can be tested in the same conditions as single-algorithm, and also that these mixed algorithms work better than single-algorithm versions - JJ

@@

% This should probably be a subsection of section 5, where you describe what any user needs to do to get this running and you  talk about reproducibility - JJ

% This is only an idea of the section
%

% First you have to say that cloud is a way of describing deployment to any kind
% of infrastructure in a reproducible way, and it needn't be in the cloud proper,
% it can be deployed to anything, that's precisely the thing. But make clear that
% when you use a cloud provider, there are more options to do it... - JJ

>>>>

The results obtained by the experiments show (see Figure \ref{fig:bbob}) how
the runtime scales with dimension to reach certain target values $\Delta f$;
The color of the lines indicates the average runtime, for each target reached
at least once. A red circle without a number on top indicates the algorithm
has reached the $10^{-8}$ target on all instances for that dimension. If there
is that number, it indicates how many times the algorithm has reached
the target. Fixed values of targets $\Delta f = 10^{k}$ with $k$ colors are
given in the legend of $f_1$ in the top row, $k$ values are $[-8,-5,-3,-2,-1,0,1]$. Results
from each configuration are presented in each column, GA, PSO, and GA\&PSO
populations. % clarify which colors for every level - JJ
% colors are shown in the figure, I put a hint that is in the top row. 
% But I can list them if that is better - M

@@

Finally, the proposed PSO\&GA mixed algorithm has reached the $10^{-8}$ target
value on all functions ($f_1-f_5$) and scales well to higher dimensions, even on
$f_3$ and $f_4$ (charts on the lower rows), which are usually considered
difficult functions. This experiment also exemplifies the type of analyses that
we can perform with the results of the EvoSwarm application by reusing the COCO framework.
We also proved that multi-population algorithms can be compared under the same 
conditions, including single and multi-algorithm versions, and results show 
that the later have better performance.

% If this is what you want to prove, it's not a very strong point. Maybe it
% would be stronger if you proved that these mixed algorithms can be tested in the
% same conditions as single-algorithm, and also that these mixed algorithms work
% better than single-algorithm versions - JJ
% Ok, stated like that - M

@@
